---
title: "texmod"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{texmod}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The main function of textools is `texmod` which creates LaTeX tables for the regression output of various models. If you want to use `texmod` to create a LaTeX table, all you need is an object that is created from a model-fitting function like `lm`. 

```{r, eval = TRUE, results = "asis"}
library(textools)

iris.lm <- lm(Sepal.Length ~ Sepal.Width + Petal.Width + Species, data = iris)
texmod(iris.lm,
  title = "Linear Model for Sepal Length",
  rowlabs = c("Sepal Width", "Petal Width", "Species (versicolor)",
    "Species (setosa)", "Species (virginica)")
)
```

By default for `lm` models only the estimates, the 95% confidence intervals for the estimates and the p-values are shown. Check out the documentation to see which columns you can add.

If you want to show the output of an ANOVA instead, you can do this by setting `results = "Anova"`.

```{r, eval = TRUE, results = "asis"}
texmod(iris.lm,
  results = "Anova"
  title = "ANOVA for Sepal Length",
  rowlabs = c("Sepal Width", "Petal Width", "Species")
)
```
