---
title: "texph"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{texph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic Usage

`texph` creates LaTeX tables for post-hoc comparisons of groups or estimated marginal means compute from the package emmeans. If you want to use `texph()` to create a LaTeX table, all you need is an object that is created from a model-fitting function like `lm()`. 

```{r, eval = TRUE, results = "asis"}
library(textools)

iris.lm <- lm(Sepal.Length ~ Sepal.Width + Petal.Width + Species, 
  data = iris)
texph(iris.lm,
  variable = "Species",
  title = "Pairwise Comparisons for Sepal Length"
)
```

The parameter `variable` specifies the variable for which the pairwise comparisons are computed. For `lm` modely by default only the mean differences, their 95% confidence intervals and the p-values are shown. Check out the documentation to see which columns you can add.

If you want to show the estimated marginal means instead, you can do this by setting `pairwise = FALSE`.

```{r, eval = TRUE, results = "asis"}
texph(iris.lm,
  pairwise = FALSE,
  variable = "Species",
  title = "EM Means for Sepal Length"
)
```

# Supported Models

Currently models from the following classes are supported:

* `aov` models created from `aov()`,
* `glm` models (only with `family = binomial(link = "logit")` created from `glm()`,
* `glmerMod` models (only with `family = binomial(link = "logit")` created from `lme4::glmer()`,
* `lm` models created from `lm()`,
* `lme` models created from `nlme::lme()`,
* `lmerMod` models created from `lme4::lmer()`,
* `lmerModLmerTest` models created from `lmerTest::lmer()`.